---
title: "Format_bw_Makara"
editor: visual
---

# Intro

All beaked whale acoustic detection data must be formatted for the NOAA Fisheries Passive Acoustic Reporting System (PARS; <https://passiveacoustics.fisheries.noaa.gov/pars>). All detection data will ultimately be shared on the Passive Acoustic Cetacean Map (PACM; <https://passiveacoustics.fisheries.noaa.gov/pacm/>).

Markara is an internal passive acoustic database for NOAA Fisheries, while PARS is the public-facing data submission system. Makara includes many more fields than PARS, and both are publicly displayed on PACM.

This document takes Pamguard database files (.sqlite3) and generates data files ready to submit to Makara.

Templates are provided for the required analysis and detections tables.

```{r study-definition}

#load required packages
library(dplyr)
library(RSQLite)
library(here)
library(stringr)
library(tidyverse)

source(here('Makara','functions','read_pg_events.R'))

#define folder that contains all Pamguard databases
DBList<-dir(path='F:/Beaked_whale_data/Databases',pattern='*.sqlite3',full.names = TRUE)
#omit gliders
DBList <- DBList[!grepl("glider", basename(DBList), ignore.case = TRUE)]

#define folder that contains all GPS data
baseEffort<-'C:/Users/annes/Documents/Github/CalCurCEAS-2024-Drifter-Analysis/_data/GPS/DASBRs'

#define folder to save the data
savedir<-here('Makara','CalCurCEAS_Detections')
dir.create(savedir)

#Deployment Data Codes
DepTemplate<-read_csv(here('Makara','Templates','deployments.csv'),show_col_types = FALSE)

#Deployment Data
DeployDetails<-read_csv(here('Makara','MakaraSubmission12022025','FinalCleanedData','deployments.csv'),show_col_types = FALSE)
DeployDetails<-DeployDetails %>%
  filter(project_code=="SWFSC_CALCURCEAS_2024") 
  
#Recording Data
RecordingData<-read_csv(here('Makara','MakaraSubmission12022025','FinalCleanedData','recordings.csv'),show_col_types = FALSE)
RecordingData<-RecordingData %>%
  filter(deployment_code %in% DeployDetails$deployment_code)

#Detection Template
DetTemplate<-read_csv(here('Makara','Templates','detections.csv'),show_col_types = FALSE)

#Analysis Template
AnalysisTemplate<-read_csv(here('Makara','Templates','analyses.csv'),show_col_types = FALSE)
```

## Load and process detections from Pamguard databases

```{r process-PG-db}

#Read Event data from all databases
bwData <- purrr::map_dfr(
  DBList,
  read_pg_events,
  deployment_codes = DeployDetails$deployment_code
)

#Convert timestamp columns & calculate duration
bwData <- bwData |>
  dplyr::mutate(
    detection_start_datetime = as.POSIXct(UTC, format="%Y-%m-%d %H:%M:%OS", tz = "UTC"),
    detection_end_datetime = as.POSIXct(EventEnd, format="%Y-%m-%d %H:%M:%OS", tz = "UTC"), 
    detection_effort_secs=round(as.numeric(as.duration(interval(detection_start_datetime,detection_end_datetime))))
  )

detections <- bwData %>%
  rename('detection_sound_source_code' = 'eventType') %>% 
  dplyr::select('deployment_code','detection_start_datetime','detection_end_datetime','detection_effort_secs','detection_sound_source_code')
  
#Re-code species names
#Remove leading and trailing whitespace
detections$detection_sound_source_code <- trimws(detections$detection_sound_source_code)

detections <- detections %>%
  mutate(detection_sound_source_code = recode(detection_sound_source_code,
                          BB = "BBWH",
                          Bb = "BBWH",
                          ZC = "GOBW",
                          BW39V="HUBW",
                          BW37V="HUBW",
                          BW43 = "GTBW",
                          MS = "STBWH",
                          BW="UNME")) 
#Remove detections of "BW?", "Oo" and "Other"
detections<-detections %>%
  filter(!detection_sound_source_code %in% c('BW?','?BW','Oo','Other'))

```

## Add required fields for Detections Worksheet

```{r}
#Define variables that are the same for all detections
detections$organization_code<-'SWFSC'
detections$analysis_code<-'BEAKED_ANALYSIS'
detections$detection_call_type_code<-'OD_CLICK_FM'
# detections$detection_behavior_code<-NA #Omitting for now
# detections$detection_demographic<-NA #Omitting for now
# detections$detection_n_validated<-NA #Omitting for now
# detections$detection_n_total<-NA #Omitting for now
detections$detection_result_code<-'DETECTED' 
 
#use readr::write_csv to preserve datetime formats
readr::write_csv(detections,file=here('Makara','CalCurCEAS_Detections','detections.csv'))

```

## Create Analysis Worksheet

```{r}
analysis<-RecordingData %>%
  filter(deployment_code %in% unique(detections$deployment_code)) %>%
  select(deployment_code,recording_start_datetime,recording_end_datetime) %>%
  rename('analysis_start_datetime'='recording_start_datetime',
         'analysis_end_datetime'='recording_end_datetime')
analysis$organization_code<-'SWFSC'
analysis$analysis_code<-'BEAKED_ANALYSIS'
analysis$recording_codes<-'SOUNDTRAP_RECORDING'
analysis$analysis_sound_source_codes<-'BBWH,HUBW,BWC,GOBW,GTBW,STBWH,UNME'
analysis$analysis_granularity_code<-'EVENT_ENCOUNTER'
analysis$analysis_sample_rate_khz<-384
analysis$analysis_min_frequency_khz<-10
analysis$analysis_max_frequency_khz<-384/2
analysis$analysis_processing_code<-'POST_PROCESSED'
analysis$analysis_quality_code<-'FULLY_VALIDATED'
analysis$analysis_protocol_reference<-'Simonis et al 2020 (https://swfsc-publications.fisheries.noaa.gov/publications/CR/2020/2020Simonis3.pdf)'
analysis$analysis_release_data<-TRUE
analysis$analysis_release_pacm<-TRUE
analysis$detector_codes<-'PAMGUARD_CLICK'

# #Order columns to match the template
# analysis_reordered<-analysis %>% select(all_of(intersect(names(AnalysisTemplate), names(analysis))))

#use readr::write_csv to preserve datetime formats
readr::write_csv(analysis,file=here('Makara','CalCurCEAS_Detections','analyses.csv'))
```

## Check Makara formatting

```{r}
library(makaraValidatr)

# Validate specific tables only, in this case only deployments.csv and recordings.csv
validate_submission(here('Makara','CalCurCEAS_Detections'),tables=c('detections','analyses'))

```
